### 2017-09-15 writing/paper/sections/coincidences.tex
start on reviewer 1

    \begin{enumerate}
        \item The symmetric difference, \(R_1 \triangle R_2\), is \(\{(a,b)\}\)
        \item \(\pi \preceq \sigma^\boks{a,b}\)\label{prop:dom1:cont}
    \end{enumerate}
\end{proposition}

@@

Consider an occurrence of \(m_1\) in a permutation in \(\av{\perm{2,3,1}}\), consisting
of elements \(x\) and \(y\). If the region corresponding
to the box \((1,1)\) is empty we have an occurrence of \(m_2\). Otherwise, if there is any
increase in this box then we would have an occurrence of \(\perm{2,3,1}\),
however, since we are in \(\av{\perm{2,3,1}}\) this is not possible. This box
must therefore contain a (non-empty) decreasing subsequence.
 This gives rise to the following lemma:

\begin{lemma}
    \label{lem:incdec}
    Let \(m =(\sigma, R)\) be a mesh pattern, where the box \((a,b)\) is not
    in \(R\), and \(\pi = (\pi,\emptyset)\) be a dominating classical pattern. If
    \(\pi \preceq p^{\boks{i,j}_a}\)\\(\(\pi \preceq p^{\boks{i,j}_d}\)),
    then in any occurrence of \(m\) in a permutation \(\varrho\), the region
    corresponding to the box \((a,b)\) can only contain an decreasing
    (increasing) subsequence of \(\varrho\).
\end{lemma}
The proof is analogous to the proof of \PropositionRef{prop:dom1}.

@@

    \begin{enumerate}
        \item \(R_1 \triangle R_2 = \{(a,b)\}\)
        \item\label{prop:dom2:cond} Either one of the following hold \begin{enumerate}
                \item\label{prop:dom2:condc} \(\pi \preceq p^{\boks{a,b}_a}\) and
                        \begin{enumerate}
                            \item \((a+1,b) \in \sigma\) and \((a+1,b-1)\notin R\) and \\
                                \((x,b-1)\in R \implies (x,b) \in R \) (where \(x\neq a,a+1\)) and\\
                                  \((a+1,y)\in R \implies (a,y) \in R\) (where \(y\neq b-1,b\)).
                            \item \((a,b+1) \in \sigma\) and \((a-1,b+1)\notin R\) and \\
                                  \((x,b+1)\in R \implies (x,b) \in R\) (where \(x\neq a-1,a\)) and\\
                                  \((a-1,y)\in R \implies (a,y) \in R\) (where \(y\neq b,b+1\)).
                        \end{enumerate}
                    \item \(\pi \preceq p^{\boks{a,b}_d}\) and
                        \begin{enumerate}
                            \item \((a+1,b+1) \in \sigma\) and \((a+1,b+1)\notin R\) and \\
                                  \((x,b+1)\in R \implies (x,b) \in R\) (where \(x\neq a,a+1\)) and\\
                                  \((a+1,y)\in R \implies (a,y) \in R\) (where \(y\neq b,b+1\)).
                            \item \((a,b) \in \sigma\) and \((a-1,b-1)\notin R\) and \\
                                  \((x,b-1)\in R \implies (x,b) \in R\) (where \(x\neq a-1,a\)) and\\
                                  \((a-1,y)\in R \implies (a,y) \in R\)  (where \(y\neq b-1,b\)).
                        \end{enumerate}
                \end{enumerate}
    \end{enumerate}
\end{proposition}
\begin{proof}
    Assume without meaningful loss of generality that \(R_2 = R_1 \cup \{(a,b)\}\).
    By \NoteRef{not:downcmesh} we only need to show that an occurrence of \(m_1\)
    implies an occurrence of \(m_2\).
    We consider taking the first branch of every choice in condition~\eqref{prop:dom2:cond}.
    Now consider a permutation \(\omega \in \av{\pi}\). Suppose
    \(\omega\) contains \(m_1\) and consider the region corresponding to
    \((a,b)\) in \(R_1\). If the region is empty, the occurrence of \(m_1\) is trivially an occurrence
    of \(m_2\).
    If the region is non-empty, then by \LemmaRef{lem:incdec} and
    condition~\eqref{prop:dom2:condc} of the proposition it must contain
    a decreasing subsequence.
    We can choose the topmost point in the region to replace the corresponding
    point in the mesh pattern and the points from the subsequence are now in
    the box southeast of the point. The other conditions allow this to be done
    without points being present in regions that were shaded. Hence there are no
    points in the region corresponding to the box \((a,b)\) in the mesh
    pattern, and therefore we can shade this region. This implies that every
    occurrence of \(m_1\) in \(\av{\pi}\) is in fact an occurrence of \(m_2\)
    so \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\).

@@

\begin{proposition}[Third Dominating Pattern Rule]
    \label{prop:dom3}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\), the sets
    \(\av{\{\pi,m_1\}}\) and \(\av{\{\pi,m_2\}}\) are coincident if
    \begin{enumerate}
        \item \(R_1 \triangle R_2 = \{(a,b)\}\)
        \item\label{prop:dom3:condocc} One of the patterns in \((\sigma,R_1)^\boksall{a,b}\)
            is coincident with a mesh pattern containing an occurrence of
            \(\mperm{\sigma}{R_2}\) as a subpattern.
    \end{enumerate}
\end{proposition}
\begin{proof}
    Assume without meaningful loss of generality that \(R_2 = R_1 \cup \{(a,b)\}\).
    \NoteRef{not:downcmesh}, implies \(\av{\{\pi,m_1\}} \subseteq \av{\{\pi,m_2\}}\) as before.
    Now consider a permutation \(\sigma\) in \(\av{\pi}\) that contains an
    occurrence of \(m_1\). If the region corresponding to the box \((a,b)\)
    is empty then we have an occurrence of \(m_2\). If the region is non-empty
    then by condition~\ref{prop:dom3:condocc}  of the proposition there exists
    a pattern in \((\sigma,R_1)^\boksall{a,b}\) such that there exists an occurrence of a mesh pattern of
    length one longer than \(m_1\) in this position. This mesh pattern is
    coincident with another mesh pattern that contains an
    occurrence of \(m_2\). Hence, every occurrence of \(m_1\) leads to an occurrence
    of \(m_2\).  Thus \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\) and the
    two patterns are coincident.
\end{proof}

@@

Intuitively it is easy to see why our previous rules have no
power here. It is impossible to add a single point to a mesh pattern \((12, R)\) and
create an occurrence of \(\pi = \perm{3,2,1}\). It is also impossible to have
a position where addition of an increase, or decrease, provides extra
shading power.

>>>>

    \begin{enumerate}
        \item The mesh set \(R_2 = R_1 \cup \{(a,b)\}\)
        \item \(\pi \preceq \sigma^\boks{a,b}\)\label{prop:dom1:cont}
    \end{enumerate}
\end{proposition}

@@

Consider an occurrence of \(m_1\) in a permutation in \(\av{\perm{2,3,1}}\), consisting
of elements \(x\) and \(y\). If the region corresponding
to the box \((1,1)\) is empty we have an occurrence of \(m_2\). Otherwise, if there is any
ascent in this box then we would have an occurrence of \(\perm{2,3,1}\),
however, since we are in \(\av{\perm{2,3,1}}\) this is not possible. This box
must therefore contain a (non-empty) decreasing subsequence.
 This gives rise to the following lemma:

\begin{lemma}
    \label{lem:incdec}
    Let \(m =(\sigma, R)\) be a mesh pattern, where the box \((a,b)\) is not
    in \(R\), and \(\pi = (\pi,\emptyset)\) be a dominating classical pattern. If
    \(\pi \preceq m^{\boks{a,b}_a}\)\\(\(\pi \preceq m^{\boks{a,b}_d}\)),
    then in any occurrence of \(m\) in a permutation \(\varrho\), the region
    corresponding to the box \((a,b)\) can only contain an decreasing
    (increasing) subsequence of \(\varrho\).
\end{lemma}
The proof is analogous to the proof of \PropositionRef{prop:dom1}.

@@

    \begin{enumerate}
        \item The mesh set \(R_2 = R_1 \cup \{(a,b)\}\)
        \item\label{prop:dom2:cond} Any one of the following four conditions hold \begin{enumerate}
                \item\label{prop:dom2:condc} \(\pi \preceq \sigma^{\boks{a,b}_a}\) and
                        \begin{enumerate}
                            \item \((a+1,b) \in \sigma\) and \((a+1,b-1)\notin R_1\) and \\
                                \((x,b-1)\in R_1 \implies (x,b) \in R_1 \) (where \(x\neq a,a+1\)) and\\
                                  \((a+1,y)\in R_1 \implies (a,y) \in R_1\) (where \(y\neq b-1,b\)).
                            \item \((a,b+1) \in \sigma\) and \((a-1,b+1)\notin R_1\) and \\
                                  \((x,b+1)\in R_1 \implies (x,b) \in R_1\) (where \(x\neq a-1,a\)) and\\
                                  \((a-1,y)\in R_1 \implies (a,y) \in R_1\) (where \(y\neq b,b+1\)).
                        \end{enumerate}
                    \item \(\pi \preceq \sigma^{\boks{a,b}_d}\) and
                        \begin{enumerate}
                            \item \((a+1,b+1) \in \sigma\) and \((a+1,b+1)\notin R_1\) and \\
                                  \((x,b+1)\in R_1 \implies (x,b) \in R_1\) (where \(x\neq a,a+1\)) and\\
                                  \((a+1,y)\in R_1 \implies (a,y) \in R_1\) (where \(y\neq b,b+1\)).
                            \item \((a,b) \in \sigma\) and \((a-1,b-1)\notin R_1\) and \\
                                  \((x,b-1)\in R_1 \implies (x,b) \in R_1\) (where \(x\neq a-1,a\)) and\\
                                  \((a-1,y)\in R_1 \implies (a,y) \in R_1\)  (where \(y\neq b-1,b\)).
                        \end{enumerate}
                \end{enumerate}
    \end{enumerate}
\end{proposition}
\begin{proof}
    By \NoteRef{not:downcmesh} we only need to show that an occurrence of \(m_1\)
    implies an occurrence of \(m_2\).
    We consider taking the first branch of every choice in condition~\eqref{prop:dom2:cond}.
    Now consider a permutation \(\omega \in \av{\pi}\). Suppose
    \(\omega\) contains \(m_1\) and consider the region corresponding to
    \((a,b)\) in \(R_1\). If the region is empty, the occurrence of \(m_1\) is trivially an occurrence
    of \(m_2\).

    If the region is non-empty, then by \LemmaRef{lem:incdec} and
    condition~\eqref{prop:dom2:condc} of the proposition it must contain
    a decreasing subsequence.
    We can choose the topmost point in the region to replace the corresponding
    point in the mesh pattern and the points from the subsequence are now in
    the box southeast of the point.

    The conditions on the mesh ensure that no elements of the permutation
    that were inside a region corresponding to an unshaded box in the occurrence
    of \(m_1\) would be in a region corresponding to a shaded box in an occurrence of
    \(m_2\).

    Hence there are no
    points in the region corresponding to the box \((a,b)\) in the mesh
    pattern, and therefore we can shade this region. This implies that every
    occurrence of \(m_1\) in \(\av{\pi}\) is in fact an occurrence of \(m_2\)
    so \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\).

@@

\begin{proposition}[Third Dominating Pattern Rule]
    \label{prop:dom3}
    Given two mesh patterns \(m_1 =(\sigma, R_1)\) and \(m_2 = (\sigma, R_2)\),
    and a dominating classical pattern \(\pi = (\pi,\emptyset)\), the sets
    \(\av{\{\pi,m_1\}}\) and \(\av{\{\pi,m_2\}}\) are coincident if
    \begin{enumerate}
        \item The mesh set \(R_2 = R_1 \cup \{(a,b)\}\)
        \item\label{prop:dom3:condocc} One of the patterns in \((\sigma,R_1)^\boksall{a,b}\)
            is coincident with a mesh pattern containing an occurrence of
            \(\mperm{\sigma}{R_2}\) as a subpattern.
    \end{enumerate}
\end{proposition}
\begin{proof}
    Assume without meaningful loss of generality that \(R_2 = R_1 \cup \{(a,b)\}\).
    \NoteRef{not:downcmesh}, implies \(\av{\{\pi,m_1\}} \subseteq \av{\{\pi,m_2\}}\) as before.
    Now consider a permutation \(\sigma\) in \(\av{\pi}\) that contains an
    occurrence of \(m_1\). If the region corresponding to the box \((a,b)\)
    is empty then we have an occurrence of \(m_2\). If the region is non-empty
    then by condition~\ref{prop:dom3:condocc}  of the proposition there exists
    a pattern in \((\sigma,R_1)^\boksall{a,b}\) such that there exists an occurrence of a mesh pattern of
    length one longer than \(m_1\) in this position. This mesh pattern is
    coincident with another mesh pattern that contains an
    occurrence of \(m_2\). Hence, every occurrence of \(m_1\) leads to an occurrence
    of \(m_2\).  Thus \(\av{\{\pi,m_2\}} \subseteq \av{\{\pi,m_1\}}\) and the
    two patterns are coincident.
\end{proof}

@@

Intuitively it is easy to see why our previous rules have no
power here. It is impossible to add a single point to a mesh pattern \((12, R)\) and
create an occurrence of \(\pi = \perm{3,2,1}\). It is also impossible to have
a position where addition of an ascent, or descent, provides extra
shading power.

### 2017-09-15 writing/paper/sections/wilf.tex
start on reviewer 1

\subsection{Wilf-classes with mesh patterns of length 1.}
When considering the mesh patterns of length \(2\) it will be useful to know
the Wilf-equivalence classes of the mesh patterns of length \(1\) inside
\(\av{\perm{2,3,1}}\), this means that we are considering the set
\(\av{\{\perm{2,3,1},p}\}\)
where \(p\) is a mesh-pattern of length 1.

@@

\nextvar[\varfine]
It can be shown by use of \PropositionRef{prop:dom2} that the patterns
\textpattern{}{1}{0/0,1/1} and \(q_1 = \textpattern{}{1}{0/0,0/1,1/1}\) are
coincident. Consider the decomposition of a non-empty avoider of \(q_1\) in
\(\av{\perm{2,3,1}}\) around the maximum:
\begin{equation*}
    \scriptvar_1 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
This can be explained succinctly by the fact that a permutation containing
\(q_1\) starts with its maximum, and by not allowing the lower-left section of the
\(\perm{2,3,1}\) avoider to be empty we prevent an occurrence from ever
happening.

Consider \(q_2 = \textpattern{}{1}{0/1,1/0,1/1}\). Avoiding this pattern
means that a permutation does not end with its maximum. We can perform a
similar
decomposition as before to get
\begin{equation*}
    \mathcal{\var}_2 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}
The pattern \(q_3 = \textpattern{}{1}{0/0,0/1,1/0}\) is the reverse-complement-inverse
of \(q_2\) and hence the avoiders of \(q_2\) and \(q_3\) are equinumerous.
All of these classes have the same generating function, namely
\begin{equation}
    \var(x) = 1 + xC(x)(C(x)-1). \label{eqn:maxlgen}
\end{equation}
The coefficients of this generating function are
\begin{equation*}
    1, 0, 1, 3, 9, 28, 90, 297, 1001, 3432, 11934,\dotsc
\tag{\href{https://oeis.org/A000245}{OEIS: A000245} with offset \(1\)}
\end{equation*}

@@

Considering an occurrence of either of these patterns in a permutation  we know
the following about the points corresponding to the points in the patterns.
\begin{itemize}
    \item The point corresponding to the first point in both patterns
        must lie in the first block of the set partition (there are
        no points southwest from it in the permutation).
    \item The point corresponding to the second point in both patterns
        is a block bottom (there are no points southeast of it in
        the permutation).
    \item If the region corresponding to box \((2,2)\) in an occurrence of
    \(m_1\) is empty, then the point corresponding to the second point is
    precisely the last block bottom. If the region corresponding to box \((0,1)\)
    in an occurrence of \(m_2\) is empty, then the point corresponding to the
    second point is precisely the first block bottom.
    If these regions are non-empty then the block containing the point
    corresponding to the second point in both patterns contains only that point
    (it is a singleton block).
\end{itemize}

@@

The classes defined by containment of \(m_1\) and \(m_2\) are
equinumerous  and therefore so are their avoiders.

Consider an avoider of \(\perm{2,3,1}\) and \(m_3\). We can perform
the decomposition around the maximum
\begin{equation*}
    \scriptvar_1 = \varepsilon \sqcup
    \decompmax{1/0,0/1}{\scriptvar_1}{}{}{\mathcal{\varmaxl}_1}
\end{equation*}
Only the first point in the top right region can
create an occurrence of \(m_3\) if and only if it is the
element with largest value in this region, therefore the partial permutation
in this region must avoid starting with the maximum.

Looking at avoiders of \(\perm{2,3,1}\) and \(m_4\) we
can perform a similar decomposition around the maximum to get
\begin{equation*}
    \scriptvar_2 = \varepsilon \sqcup
    \decompmax{1/0,0/1}{\scriptvar_2}{}{}{\mathcal{\varmaxl}_3}
\end{equation*}
An occurrence of \(m_4\) can never occur in the
top right region. It could only occur between the maximum and the first point
in the region, if and only if this first point is the lowest valued element in
this region.
Since both \(\mathcal{\varmaxl}_1\) and \(\mathcal{\varmaxl}_3\) have the same
enumeration, \(\scriptvar_1\) and \(\scriptvar_2\) must also have
the same enumeration and are therefore Wilf-equivalent.

Now we must consolidate these two subclasses. In order to do this we must
consider the decomposition around the leftmost point of a permutation in
\(\av{\{\perm{2,3,1},m_1\}}\). We have the following
\begin{equation*}
    \scriptvar_3 = \varepsilon \sqcup
    \decompleft{1/0,0/1}{\scriptvar_3}{}{}{\mathcal{\varmaxl}_3}
\end{equation*}
It is therefore obvious that avoiders of \(m_1\) and avoiders of \(m_4\)
have the same enumeration, and therefore all four patterns are Wilf-equivalent
in \(\av{\perm{2,3,1}}\) with generating function satisfying
\begin{equation*}
    \var(x) = 1 + x\var(x)\varmaxl(x)
\end{equation*}
where \(\varmaxl(x)\) is the generating function given in \EquationRef{eqn:maxlgen}.
This can be enumerated to give the sequence
\begin{equation*}
    1, 1, 1, 2, 6, 19, 61, 200, 670, 2286, 7918,\dotsc \tag{\href{https://oeis.org/A035929}{OEIS: A035929} offset 1}
\end{equation*}

% This particular example is interesting as it shows that both methods can be used in tandem to establish a coincidence class.

>>>>

\subsection{Wilf-classes with mesh patterns of length 1.}
\label{wilf1}
When considering the mesh patterns of length \(2\) it will be useful to know
the Wilf-equivalence classes of the mesh patterns of length \(1\) inside
\(\av{\perm{2,3,1}}\), this means that we are considering the set
\(\av{\{\perm{2,3,1},p}\}\)
where \(p\) is a mesh-pattern of length 1.

@@

\nextvar[\varfine]
It can be shown by use of \PropositionRef{prop:dom2} that the patterns
\textpattern{}{1}{0/0,1/1} and \(q_1 = \textpattern{}{1}{0/0,0/1,1/1}\) are
coincident inside \(\av{\perm{2,3,1}}\). Consider the decomposition of a non-empty avoider of \(q_1\) in
\(\av{\perm{2,3,1}}\) around the maximum:
\begin{equation*}
    \scriptvar_1 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}\setminus\varepsilon}{}{}{\mathcal{C}}
\end{equation*}
This can be explained succinctly by the fact that a permutation containing
\(q_1\) starts with its maximum, and by not allowing the lower-left section of the
\(\perm{2,3,1}\) avoider to be empty we prevent an occurrence from ever
happening.

Consider \(q_2 = \textpattern{}{1}{0/1,1/0,1/1}\). Avoiding this pattern
means that a permutation does not end with its maximum. We can perform a
similar
decomposition as before to get
\begin{equation*}
    \mathcal{\var}_2 =\varepsilon \sqcup
\decompmax{0/1,1/0}{\mathcal{C}}{}{}{\mathcal{C}\setminus\varepsilon}
\end{equation*}
The pattern \(q_3 = \textpattern{}{1}{0/0,0/1,1/0}\) is the reverse-complement-inverse
of \(q_2\) and hence the avoiders of \(q_2\) and \(q_3\) (\(\scriptvar_2\) and \(\scriptvar_3\)) are equinumerous.
All of these classes have the same generating function, namely
\begin{equation}
    \var(x) = 1 + xC(x)(C(x)-1). \label{eqn:maxlgen}
\end{equation}
The coefficients of this generating function are
\begin{equation*}
    1, 0, 1, 3, 9, 28, 90, 297, 1001, 3432, 11934,\dotsc
\tag{\href{https://oeis.org/A000245}{OEIS: A000245} with offset \(1\)}
\end{equation*}

@@

Considering an occurrence of either of these patterns in a permutation  we know
the following about the points corresponding to the points in the patterns.
\begin{itemize}
    \item The point corresponding to the first point in both patterns
        must lie in the first block of the set partition (there are
        no points southwest from it in the permutation).
    \item The point corresponding to the second point in both patterns
        is a block bottom (there are no points southeast of it in
        the permutation).
    \item If the region corresponding to box \((2,2)\) in an occurrence of
    \(m_1\) is empty, then the point corresponding to the second point is
    precisely the last block bottom. If the region corresponding to box \((1,0)\)
    in an occurrence of \(m_2\) is empty, then the point corresponding to the
    second point is precisely the first block bottom.
    If these regions are non-empty then the block containing the point
    corresponding to the second point in both patterns contains only that point
    (it is a singleton block).
\end{itemize}

@@

The classes defined by containment of \(m_1\) and \(m_2\) inside \(\av{\perm{2,3,1}}\)are
equinumerous and therefore so are their avoiders.

Consider the class, \(\scriptvar_3\), of permutations defined by avoiding \(\perm{2,3,1}\) and \(m_3\). We can decompose a member of this class around the maximum
\begin{equation*}
    \scriptvar_3 = \varepsilon \sqcup
    \decompmax{1/0,0/1}{\scriptvar_3}{}{}{\mathcal{\varmaxl}_1}
\end{equation*}
Only the first point in the top right region can
create an occurrence of \(m_3\) if and only if it is the
element with largest value in this region, therefore the partial permutation
in this region must avoid starting with the maximum.

Looking at avoiders of \(\perm{2,3,1}\) and \(m_4\) we
can perform a similar decomposition around the maximum to get
\begin{equation*}
    \scriptvar_4 = \varepsilon \sqcup
    \decompmax{1/0,0/1}{\scriptvar_4}{}{}{\mathcal{\varmaxl}_3}
\end{equation*}
An occurrence of \(m_4\) can never occur in the
top right region. It could only occur between the maximum and the first point
in the region, if and only if this first point is the lowest valued element in
this region, so this top right region must contain a sub-permutation that does not
start with it's minimum, i.e., it is a member of \(\mathcal{\varmaxl}_3\) described
in \SectionRef{wilf1}.
Since both \(\mathcal{\varmaxl}_1\) and \(\mathcal{\varmaxl}_3\) have the same
enumeration, \(\scriptvar_3\) and \(\scriptvar_4\) must also have
the same enumeration and are therefore Wilf-equivalent.

Now we must consolidate these two subclasses. In order to do this we must
consider the decomposition around the leftmost point of a permutation in
\(\av{\{\perm{2,3,1},m_1\}}\). We have the following
\begin{equation*}
    \scriptvar_1 = \varepsilon \sqcup
    \decompleft{1/0,0/1}{\scriptvar_1}{}{}{\mathcal{\varmaxl}_3}
\end{equation*}
It is therefore obvious that avoiders of \(m_1\) and avoiders of \(m_4\)
have the same enumeration, and therefore all four patterns are Wilf-equivalent
in \(\av{\perm{2,3,1}}\) with generating function satisfying
\begin{equation*}
    \var(x) = 1 + x\var(x)\varmaxl(x)
\end{equation*}
where \(\varmaxl(x)\) is the generating function given in \EquationRef{eqn:maxlgen}.
This can be enumerated to give the sequence
\begin{equation*}
    1, 1, 1, 2, 6, 19, 61, 200, 670, 2286, 7918,\dotsc \tag{\href{https://oeis.org/A035929}{OEIS: A035929} offset 1}
\end{equation*}
